---
title: "Tab 2"
author: "Barbara Rose Hoover"
date: "3/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(shiny)
library(sf)
library(leaflet)
library(tidyverse)
```

#california county shape files
```{r}
county<-read_sf(dsn = ".", layer = "california_county_shape_file") # Read data
st_crs(county) = 4326 

ca_county<-county %>% 
  select(1,2,7,10) %>%
  rename(county=`NAME`)  
```

#rent data
```{r}
rent<-rent_county %>% 
  select(-`X1`, -`FIPS`) %>% 
  gather(bedroom, cost, -county) %>% 
  group_by(county) %>% 
  mutate(mean.rent=mean(cost))
```

#Mountain and Coast data
1)Filtering business code for places with ski resorts
2)combine with coast data
```{r}
ca_naics<-read_csv("ca_naics_code.csv")


#filtering for ski resorts (NAICS code = 713920)
ski_ca<- ca_naics %>% 
  filter(naics == 713920) %>% #filter to get only counties with ski resorts to identify mountains
  transform(fipscty = as.numeric(fipscty)) %>% 
  rename(fips=fipscty) %>% 
  transform(est = "mountain") %>% 
  rename(mt=est) 

geo<-ski_ca %>% 
  full_join(county_fips, by="fips") %>% #adding county neames to mountain data
  full_join(coast, by="county") %>% #combining rows for coast and mountain into one row names "coast_mountain"
  replace_na(list(mt = "", coast = "")) %>% 
  unite("geo", "mt", "coast", remove = TRUE, sep="") %>% #combine coast and mountain into one column
  select(county, geo)
```
write csv for reference
```{r}
write.csv(geo, file="Coast or Mountain Classification.csv", row.names = FALSE)
```

#Rural vs Urban

```{r data}
#https://www.cdc.gov/nchs/data_access/urban_rural.htm
#https://www.cdc.gov/nchs/data_access/urban_rural.htm#Data_Files_and_Documentation

```
Classification Guide
```{r}
#Classification: https://www.cdc.gov/nchs/data/data_acces_files/NCHSUrbruralFileDocumentationInternet2.pdf

code<-c(1,2,3,4,5,6)
class<-c("Large central metro", "Large fringe metro", "Medium metro", "Small metro", "Micropolitan", "Noncore")
metro_code<-data.frame(code, class)
```
making data frame for CA only with relevant columns 
```{r}
urb_rur<-NCHSURCodes2013 %>%
  rename(county=`County name`) %>% 
  rename(fips=`FIPS code`) %>%
  rename(code=`2013 code`) %>% 
  filter(`State Abr.`=="CA") %>%
  transform(fips = fips-6000) %>% 
  select(1,3,4,7) %>% 
  lapply(gsub, pattern=' County', replacement='') %>% 
  data.frame(stringsAsFactors = FALSE) %>% 
  transform(code = as.numeric(code)) %>%
  mutate(metro=ifelse(code>=4, "rural", "city"))#classify rural and city
```

Assigning classification to codes in urb_rur
```{r}
metro<-urb_rur %>% 
  full_join(metro_code, by = "code") %>% 
  rename(metro_code=code) %>% 
  rename(metro_class=class)
```
Save as csv
```{r}
write.csv(metro, file="Urban Rural Classification.csv", row.names = FALSE)
```

#Combining Coastal/Mt and Urban/Rural data
```{r}
metro_geo<-full_join(metro, geo, by="county")
```

#Combining rent, Coastal/Mt and Urban/Rural data
```{r}
rent_metro_geo<-full_join(rent, metro_geo, by="county")
```

#Combining rent, Coastal/Mt and Urban/Rural data, county shape file

```{r}
tab_2<-full_join(ca_county, rent_metro_geo, by="county")
```
#saving as csv
```{r}
st_write(tab_2, "tab_2.shp")
```

-----------------------------------------
#coast or mt UI
```{r}
  radioButtons("geo", label = h3("Beach or Slopes"),
    choices = list("Coast" = "coast", "Mountains" = "mountains", "Don't Care" = "na"), 
    selected = "na")
```

#urban or rural UI
```{r}
  radioButtons("metro", label = h3("Big City or Small Town"),
    choices = list("City" = "city", "Rural" = "rural", "Don't Care" = "na"), 
    selected = "na")
```

#Rent: BEDRoom
```{r}
checkboxGroupInput("bedrm", label = h3("How Many Bed Rooms?"), 
    choices = list("Studio" = "studio", "One Bed Room" = "one_bed", "Two Bed Room" = "two_bed", "Three Bed Room" = "three_bed"),
    selected = "studio")
```

#Price
```{r}
sliderInput("rent", label = h3("Max Rent Budget"), min = 0, 
        max = 4000, value = 1000)
```


```{r}
output$map <- renderLeaflet({

    dat <- tab_2
    
    #filter for coast/mountain
    if(input$geo != "na"){
        dat <- dat[which(dat$coast_mountain == input$geo),]

    }
    #filter for metro classification
    if(input$metro != "na"){
        dat <- dat[which(dat$metro == input$metro),]

    }
    #filter for bedrooms and rent max
    dat_rent<-dat %>%
      filter(bedroom %in% input$bedrm) %>% 
      filter(cost <= input$rent)
    
    #create map
    leaflet() %>% 
      addTiles() %>% 
      addPolygons(data = dat_rent)
      

})
```




```{r}
tab_2<-read_sf(dsn = ".", layer = "tab_2") # Read data
st_crs(tab_2) = 4326 
colnames(tab_2)
```


